Out-of-Sample Comparisons of Overfit Models

### 2013-12-20 paper.tex
Tweak a few statements in setup section

The forecaster observes the data $(y_t,x_t)$ for periods 1 through $T$
and divides them into an estimation sample of the first $R$
observations and a test sample of the remaining $P$ observations.
After choosing one of the models, the forecaster will use that model
to make predictions for periods $T + h + 1$ through $T + h + Q$, where
$Q$ is a known positive integer.  The forecaster's goal is to choose
the model that will have lower average loss over periods $T+h$ through
$T+h+Q$, evaluated by the known loss function $L$.  We allow $Q = 1$,
so this setup generalizes the problem of choosing a model for a single
prediction.

>>>>

The forecaster observes the data $(y_t,x_t)$ for periods 1 through $T$
and divides them into an estimation sample of the first $R$
observations and a test sample of the remaining $P$ observations.
After choosing one of the models, the forecaster will use that model
to make predictions for periods $T + h + 1$ through $T + h + Q$, where
$Q$ is a known positive integer.  The forecaster's goal is to choose
the model that will have lower average loss over periods $T+h+1$ through
$T+h+Q$, evaluated by the known loss function $L$.  We allow $Q = 1$,
so this setup generalizes the problem of choosing a model for a single
prediction.
